Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-10-01 prob.tex
prob.tex Fixing citations...

Although specifying a probability measure for every event looks complex,
it can be simply constructed by 
\begin{equation}
\pmeas(E)=\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum f(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
\end{equation}
where $f:\Omega\rightarrow[0,1]$, $\sideset{_{\mathbb{R}}}{_{\omega\in\Omega}}\sum f(\omega)=1$,
and $f$ is called the Radon-Nikodym derivative of $\pmeas$ (with
respect to the counting measure)~\cite{Nikodym1930,Folland2013}.
The converse is also valid and called the Radon-Nikodym theorem.

@@

As motivated above, an event $E_{1}$ may have an interval of probability
$[l_{1},r_{1}]$. Assume that another disjoint event $E_{2}$ has
interval probability $[l_{2},r_{2}]$, what is the interval probability
of the event $E_{1}\cup E_{2}$? The answer is somewhat subtle: although
it is possible to use the sum of the intervals $[l_{1}+l_{2},r_{1}+r_{2}]$
as the combined probability, one can do find a much tighter interval
if information \emph{against} the event (i.e., information about the
complement event) is also taken into consideration. Formally, for
a general event $E$ with probability $[l,r]$, the evidence that
contradicts $E$ is an evidence supporting the complement of $E$.
The complement of $E$ must therefore have probability $\left[1-r,1-l\right]$
which we abbreviate $\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\left[l,r\right]$,
where the preposing $\mathscr{I}$ specifies we subtract intervals.
Given a collection of intervals $\mathscr{I}$, an $\mathscr{I}$\textendash interval-valued
probability measure is a function $\bar{\mu}:\events\rightarrow\mathscr{I}$
such that~\cite{JamisonLodwick2004}:\footnote{The right-end of the interval-valued probability measure is a special
case of (sub-additive) capacity~\cite{Choquet1954,Graf1980,Goodman2013}
or outer measure~\cite{Folland2013}. The left-end of the interval-valued
probability measure is a special case of game~\cite{Shapley1965}.} 
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$. 
\item $\bar{\mu}(\Omega)=[1,1]$. 
\item For every collection of pairwise disjoint events $\left\{ E_{i}\right\} _{i=1}^{N},\left\{ E_{i}'\right\} _{i=1}^{N'}\subseteq\events$
with $\Omega=\left(\bigcup_{i=1}^{N}E_{i}\right)\bigcup\left(\bigcup_{i=1}^{N'}E_{i}'\right)$,
we have 
\[
\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\left[\max\left\{ 1-\sideset{_{\mathbb{R}}}{_{i=1}^{N'}}\sum r_{i}',\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum l_{i}\right\} ,\min\left\{ 1-\sideset{_{\mathbb{R}}}{_{i=1}^{N'}}\sum l_{i}',\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum r_{i}\right\} \right]\textrm{ ,}
\]
where $\bar{\mu}\left(E_{i}\right)=[l_{i},r_{i}]$ and $\bar{\mu}\left(E_{i}'\right)=[l_{i}',r_{i}']$
for all $i$.
\end{itemize}
In order to understand this definition, we tear the last condition
apart and provide an equivalent definition of interval-valued probability
measures.

@@

In contrast to real-valued probability measures, there is no easy
Radon-Nikodym theorem to simplify an interval-valued probability measure
to its Radon-Nikodym derivative. So far, the interval-valued Radon-Nikodym
Theorems are either too restricted to apply to all interval-valued
probability measures~\cite{Choquet1954,Graf1980,Goodman2013} or
corresponding an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
to another set function~$\bar{f}:\events\rightarrow\bar{\mathscr{I}}$
which is not as simple as the original Radon-Nikodym derivative~\cite{GilboaSchmeidler1994,Goodman2013}.

@@

\begin{definition}~Given an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
\begin{itemize}
\item A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \textrm{probability measure }\pmeas:\events\rightarrow[0,1]\middle|\forall E\in\events.\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\} $
\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}.
\item $\bar{\mu}$ is called \emph{convex}, \emph{2-monotone}, or\emph{
supermodular} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014,Grabisch2016}.\footnote{\yutsung{In order to simplify the discussion, let $l$ be the left-end
of an interval-valued probability measure~$\bar{\mu}$. Because of
equation~(\ref{eq:ClassicalInterval-valuedProbability-Complement}),
$\bar{\mu}$ is convex if and only if 
\begin{equation}
l\left(E_{1}\cup E_{2}\right)+l\left(E_{1}\cap E_{2}\right)\ge l\left(E_{1}\right)+l\left(E_{2}\right)\textrm{ ,}\label{eq:convex-game}
\end{equation}
which is a special case of the Dempster-Shafer condition
\begin{equation}
l\left(\bigcup_{i=1}^{N}E_{i}\right)\ge\sum_{I\subseteq\left\{ 1,\ldots,N\right\} }\left(-1\right)^{\left|I\right|+1}l\left(\bigcap_{i\in I}E_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game}
\end{equation}
Therefore, in order to understand the meaning of equation~(\ref{eq:convex-game}),
we could try to understand meaning of the Dempster-Shafer belief function.
Unfortunately, when people introduce the Dempster-Shafer theory, they
usually don't start from equation~(\ref{eq:Dempster-Shafer-game}).
Instead, they introduce a basic belief assignment~$m\left(E\right)=\sum_{E'\subseteq E}\left(-1\right)^{\left|E\setminus E'\right|}l\left(E'\right)$
first, and $m\left(E\right)$ represents the belief committed to the
event~$E$ and only to it, in the sense that it could not be committed
to any proper subset of $A$~\cite{Grabisch2016}. Then, equation~(\ref{eq:Dempster-Shafer-game})
is equivalent to $m\left(E\right)\ge0$ for all $E$~\cite{Grabisch2016},
and the non-negative of $m\left(E\right)$ is intuitive.

@@

It is common to consider convex interval-valued probability measures.
For example, a special case of convex interval-valued probability
measures consists the Dempster-Shafer belief function as the left-end
and the Dempster-Shafer plausibility as the right-end~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Goodman2013,Teran2014}.
Dempster-Shafer functions, also called \emph{completely} or \emph{totally
monotone}, plays an important role in the theory of non-additive belief.
Furthermore, convex interval-valued probability measures have a good
property that they can always be associated with real-valued probability
measures.

>>>>

Although specifying a probability measure for every event looks complex,
it can be simply constructed by 
\begin{equation}
\pmeas(E)=\sideset{_{\mathbb{R}}}{_{\omega\in E}}\sum f(\omega)\textrm{ ,}\label{eq:Radon-Nikodym}
\end{equation}
where $f:\Omega\rightarrow[0,1]$, $\sideset{_{\mathbb{R}}}{_{\omega\in\Omega}}\sum f(\omega)=1$,
and $f$ is called the Radon-Nikodym derivative of $\pmeas$ (with
respect to the counting measure)~\cite{Nikodym1930,Folland1999}.
The converse is also valid and called the Radon-Nikodym theorem.

@@

As motivated above, an event $E_{1}$ may have an interval of probability
$[l_{1},r_{1}]$. Assume that another disjoint event $E_{2}$ has
interval probability $[l_{2},r_{2}]$, what is the interval probability
of the event $E_{1}\cup E_{2}$? The answer is somewhat subtle: although
it is possible to use the sum of the intervals $[l_{1}+l_{2},r_{1}+r_{2}]$
as the combined probability, one can do find a much tighter interval
if information \emph{against} the event (i.e., information about the
complement event) is also taken into consideration. Formally, for
a general event $E$ with probability $[l,r]$, the evidence that
contradicts $E$ is an evidence supporting the complement of $E$.
The complement of $E$ must therefore have probability $\left[1-r,1-l\right]$
which we abbreviate $\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\left[l,r\right]$,
where the preposing $\mathscr{I}$ specifies we subtract intervals.
Given a collection of intervals $\mathscr{I}$, an $\mathscr{I}$\textendash interval-valued
probability measure is a function $\bar{\mu}:\events\rightarrow\mathscr{I}$
such that~\cite{JamisonLodwick2004}:\footnote{The right-end of the interval-valued probability measure is a special
case of (sub-additive) capacity~\cite{Choquet1954,Graf1980,Goodman1997}
or outer measure~\cite{Folland1999}. The left-end of the interval-valued
probability measure is a special case of (super-additive cooperative)
game~\cite{Shapley1971,Grabisch2016}.} 
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$. 
\item $\bar{\mu}(\Omega)=[1,1]$. 
\item For every collection of pairwise disjoint events $\left\{ E_{i}\right\} _{i=1}^{N},\left\{ E_{i}'\right\} _{i=1}^{N'}\subseteq\events$
with $\Omega=\left(\bigcup_{i=1}^{N}E_{i}\right)\bigcup\left(\bigcup_{i=1}^{N'}E_{i}'\right)$,
we have 
\[
\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\left[\max\left\{ 1-\sideset{_{\mathbb{R}}}{_{i=1}^{N'}}\sum r_{i}',\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum l_{i}\right\} ,\min\left\{ 1-\sideset{_{\mathbb{R}}}{_{i=1}^{N'}}\sum l_{i}',\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum r_{i}\right\} \right]\textrm{ ,}
\]
where $\bar{\mu}\left(E_{i}\right)=[l_{i},r_{i}]$ and $\bar{\mu}\left(E_{i}'\right)=[l_{i}',r_{i}']$
for all $i$.
\end{itemize}
In order to understand this definition, we tear the last condition
apart and provide an equivalent definition of interval-valued probability
measures.

@@

In contrast to real-valued probability measures, there is no easy
Radon-Nikodym theorem to simplify an interval-valued probability measure
to its Radon-Nikodym derivative. So far, the interval-valued Radon-Nikodym
Theorems are either too restricted to apply to all interval-valued
probability measures~\cite{Choquet1954,Graf1980,Goodman1997} or
corresponding an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
to another set function~$\bar{f}:\events\rightarrow\bar{\mathscr{I}}$
which is not as simple as the original Radon-Nikodym derivative~\cite{GilboaSchmeidler1994,Goodman1997}.

@@

\begin{definition}~Given an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
\begin{itemize}
\item A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \textrm{probability measure }\pmeas:\events\rightarrow[0,1]\middle|\forall E\in\events.\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\} $
\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Teran2014}.
\item $\bar{\mu}$ is called \emph{convex}, \emph{2-monotone}, or\emph{
supermodular} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
for all $E_{1},E_{2}\in\events$~\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Teran2014,Grabisch2016}.\footnote{\yutsung{In order to simplify the discussion, let $l$ be the left-end
of an interval-valued probability measure~$\bar{\mu}$. Because of
equation~(\ref{eq:ClassicalInterval-valuedProbability-Complement}),
$\bar{\mu}$ is convex if and only if 
\begin{equation}
l\left(E_{1}\cup E_{2}\right)+l\left(E_{1}\cap E_{2}\right)\ge l\left(E_{1}\right)+l\left(E_{2}\right)\textrm{ ,}\label{eq:convex-game}
\end{equation}
which is a special case of the Dempster-Shafer condition~\cite{Shafer1976,Grabisch2016}
\begin{equation}
l\left(\bigcup_{i=1}^{N}E_{i}\right)\ge\sum_{I\subseteq\left\{ 1,\ldots,N\right\} }\left(-1\right)^{\left|I\right|+1}l\left(\bigcap_{i\in I}E_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game}
\end{equation}
Therefore, in order to understand the meaning of equation~(\ref{eq:convex-game}),
we could try to understand meaning of the Dempster-Shafer belief function.
Unfortunately, when people introduce the Dempster-Shafer theory, they
usually don't start from equation~(\ref{eq:Dempster-Shafer-game}).
Instead, they introduce a basic belief assignment~$m\left(E\right)=\sum_{E'\subseteq E}\left(-1\right)^{\left|E\setminus E'\right|}l\left(E'\right)$
first, and $m\left(E\right)$ represents the belief committed to the
event~$E$ and only to it, in the sense that it could not be committed
to any proper subset of $A$. Then, equation~(\ref{eq:Dempster-Shafer-game})
is equivalent to $m\left(E\right)\ge0$ for all $E$, and the non-negative
of $m\left(E\right)$ is intuitive.

@@

It is common to consider convex interval-valued probability measures.
For example, a special case of convex interval-valued probability
measures consists the Dempster-Shafer belief function as the left-end
and the Dempster-Shafer plausibility as the right-end~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Goodman1997,Marinacci1999,Teran2014}.
Dempster-Shafer functions, also called \emph{completely} or \emph{totally
monotone}, plays an important role in the theory of non-additive belief.
Furthermore, convex interval-valued probability measures have a good
property that they can always be associated with real-valued probability
measures.
